### 2021-06-04 README.Rmd
dsfsfs

- `add_archigos()`: adds some summary variables from Archigos about political leaders for state-year or dyad-year data.
- `add_atop_alliance()`: adds ATOP alliance information to dyad-year data.
- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_ccode_to_gw()`: 	Add Correlates of War state system codes to dyad-year or state-year data with Gleditsch-Ward state codes.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_cow_mids()`: adds Correlates of War (CoW) Militarized Interstate Dispute (MID) data to dyad-year data frame
- `add_cow_trade()`: adds Correlates of War trade data to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_gml_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_igos()`: adds Correlates of War International Governmental Organizations (IGOs) data to dyad-year or state-year data.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data. (DEPRECATED)
- `add_minimum_distance()`: adds minimum distance (in kilometers) to dyad-year or state-year data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `add_peace_years()`: Add Peace Years to Your Conflict Data
- `add_sdp_gdp()`: adds estimates of (gross and surplus) domestic product and population size to dyad-year or state-year data
- `add_strategic_rivalries()`: Add Thompson and Dreyer's (2012) strategic rivalry data to dyad-year data frame
- `add_ucdp_acd()`: Add UCDP Armed Conflict Data to state-year data frame
- `add_ucdp_onsets()`: adds UCDP onsets to state-year data
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

tic()
create_dyadyears() %>%
  # Add GML MIDs 
  add_gml_mids(keep=NULL) %>%
  # Add Correlates of War MIDs 
  add_cow_mids(keep=NULL) %>%
  # add peace years
  add_peace_years() %>%
  # Add Gleditsch-Ward codes, because we can
  add_gwcode_to_cow() %>%
  # Add strategic rivalry data
  add_strategic_rivalries() %>%
  # Add trade data
  add_cow_trade() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add IGOs data
  add_igos() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # add alliance data from ATOP
  add_atop_alliance() %>%
  # add minimum distance. No default, must specify "cow" or "gw"
  add_minimum_distance(system = "cow") %>%
  # add Archigos data
  add_archigos() %>%
  # add gross and surplus GDP data
  add_sdp_gdp(system = "cow") %>%
  # add terrain ruggedness data, if you wanted it
  add_rugged_terrain() %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()

@@

tic()
create_stateyears() %>%
  add_gwcode_to_cow() %>%
  add_ucdp_onsets() %>%
  add_capital_distance() %>%
  add_contiguity() %>%
  add_cow_majors() %>%
  add_cow_trade() %>%
  add_democracy() %>%
  add_igos() %>%
  add_minimum_distance(system = "cow") %>%
  add_archigos() %>%
  add_nmc() %>%
  add_sdp_gdp(system = "cow") 
toc()

>>>>

- `add_archigos()`: adds some summary variables from Archigos about political leaders for state-year or dyad-year data.
- `add_atop_alliance()`: adds ATOP alliance information to dyad-year data.
- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_ccode_to_gw()`: 	Add Correlates of War state system codes to dyad-year or state-year data with Gleditsch-Ward state codes.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_cow_mids()`: adds Correlates of War (CoW) Militarized Interstate Dispute (MID) data to dyad-year data frame
- `add_cow_trade()`: adds Correlates of War trade data to dyad-year or state-year data.
- `add_creg_fractionalization()`: add fractionalization/polarization estimates from CREG to your dyad-year or state-year data
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_gml_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_igos()`: adds Correlates of War International Governmental Organizations (IGOs) data to dyad-year or state-year data.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data. (DEPRECATED)
- `add_minimum_distance()`: adds minimum distance (in kilometers) to dyad-year or state-year data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `add_peace_years()`: Add Peace Years to Your Conflict Data
- `add_sdp_gdp()`: adds estimates of (gross and surplus) domestic product and population size to dyad-year or state-year data
- `add_strategic_rivalries()`: Add Thompson and Dreyer's (2012) strategic rivalry data to dyad-year data frame
- `add_ucdp_acd()`: Add UCDP Armed Conflict Data to state-year data frame
- `add_ucdp_onsets()`: adds UCDP onsets to state-year data
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

tic()
create_dyadyears() %>%
  # Add GML MIDs 
  add_gml_mids(keep=NULL) %>%
  # Add Correlates of War MIDs 
  add_cow_mids(keep=NULL) %>%
  # add peace years
  add_peace_years() %>%
  # Add Gleditsch-Ward codes, because we can
  add_gwcode_to_cow() %>%
  # Add strategic rivalry data
  add_strategic_rivalries() %>%
  # Add trade data
  add_cow_trade() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add IGOs data
  add_igos() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # add alliance data from ATOP
  add_atop_alliance() %>%
  # add minimum distance
  add_minimum_distance() %>%
  # add Archigos data
  add_archigos() %>%
  # add gross and surplus GDP data
  add_sdp_gdp() %>%
  # add terrain ruggedness data, if you wanted it
  add_rugged_terrain() %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()

@@

tic()
create_stateyears() %>%
  add_gwcode_to_cow() %>%
  add_ucdp_onsets() %>%
  add_capital_distance() %>%
  add_contiguity() %>%
  add_cow_majors() %>%
  add_cow_trade() %>%
  add_democracy() %>%
  add_igos() %>%
  add_minimum_distance() %>%
  add_archigos() %>%
  add_nmc() %>%
  add_sdp_gdp() 
toc()
